A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-10 paper/elsarticle/elsarticle-template.tex
paper

We propose a spatial AR system that produces the effect of keystone correction analytically, and that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downward toward the scene plane. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view.
\end{abstract}

@@

\begin{figure}
    \centering
    \subfloat[\centering Oblique view.]{{\includegraphics[height=4.2cm]{images/1.pdf}}}
    \qquad
    \subfloat[\centering Downwards view.]{{\includegraphics[height=4.2cm]{images/3_above3.png}}}
    \caption{The virtual camera is obtained by (i) rotating the camera (top left, black) about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. The virtual projector is obtained by (ii) rotating the projector (bottom left, black) about the point of intersection of its optical axis with the scene plane such that the optical axis be made parallel with the scene plane's normal vector, (iii) rotating the $X$- and $Y$-axes to align them with those of the virtual camera, and (iv) optionally translating along the normal direction to achieve the desired projected image dimensions.} %The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera.
    \label{fig:virtualproj}
\end{figure}

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) rotate the camera about its center of projection to align its optical axis with the normal vector of the scene plane, giving a virtual camera likewise facing directly\footnote{A physical camera placed to face downwards is likely to not face downwards precisely; in contrast, the virtual camera's optical axis is aligned exactly with the scene plane's normal vector, rendering it fronto-parallel with respect to the scene plane.} downwards to the scene plane (cf.\ Figure~\ref{fig:virtualproj}). Next, we (ii) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); then, we (iii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Finally, we (iv) align the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector (cf.\ again Figure~\ref{fig:virtualproj}). The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions. Optionally, we additionally adjust the height above the scene plane of the virtual projector, in order to satisfy desired projected image dimensions provided in metric units.

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with two variants of a baseline approach involving manual keystone correction (`Baseline A' and `Baseline B'), by aiming to place an image for each location aligned with the principal axes of the floorspace, absent projective distortions, and with the same dimensions (50~cm~$\times$~31.25~cm). Using our approach to carry out keystone correction analytically, we carried out all steps within a time budget of 15 min. Accordingly, we set 15 min to be the time budget of the first variant of the baseline approach (`Baseline A'), in which we carry out a \texit{manual} keystone correction using the software bundled with the steerable mirror system mounted alongside our projector. The second variant of the baseline approach (`Baseline B') is to again use the bundled software to carry out keystone correction manually, but to record how much time is necessary to produce augmentations within a mean tolerance of XX. All experiments were carried out jointly by the same experienced technician and assistant.

The hardware setup employed in the evaluation comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downward-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 9~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.

@@

The total amount of time to carry out all the above steps amounted to ca.\ 15 min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software.

\paragraph{Baseline A} ...

\paragraph{Baseline B} ...

>>>>

We propose a spatial AR system that produces the effect of keystone correction analytically, and that facilitates placement by enabling intuitively placing the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera facing downwards towards the scene plane. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view.
\end{abstract}

@@

\begin{figure}
    \centering
    \subfloat[\centering Oblique view.]{{\includegraphics[height=4.2cm]{images/1.pdf}}}
    \qquad
    \subfloat[\centering Downwards view.]{{\includegraphics[height=4.2cm]{images/3_above3.png}}}
    \caption{The virtual camera is obtained by (i) rotating the camera (top left, black) about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. The virtual projector is obtained by (ii) rotating the projector (bottom left, black) about the point of intersection of its optical axis with the scene plane such that the optical axis be made parallel with the scene plane's normal vector, (iii) rotating the $X$- and $Y$-axes to align them with those of the virtual camera, and optionally (iv) translating along the normal direction to achieve the desired projected image dimensions.} %The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera.
    \label{fig:virtualproj}
\end{figure}

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) rotate the camera about its center of projection to align its optical axis with the normal vector of the scene plane, giving a virtual camera likewise facing directly\footnote{A physical camera placed to face downwards is likely to not face downwards precisely; in contrast, the virtual camera's optical axis is aligned exactly with the scene plane's normal vector, rendering it fronto-parallel with respect to the scene plane.} downwards to the scene plane (cf.\ Figure~\ref{fig:virtualproj}). Next, we (ii) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane) and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Finally, we (iii) align the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector (cf.\ again Figure~\ref{fig:virtualproj}). The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions. Optionally, we additionally (iv) adjust the height above the scene plane of the virtual projector, in order to satisfy desired projected image dimensions provided in metric units.

@@

We evaluate our approach by augmenting 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Vienna, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place an image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same dimensions (50~cm~$\times$~31.25~cm). All experiments were carried out by the same experienced technician.

The hardware setup employed in the evaluation comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downward-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.

@@

The total amount of time to carry out all the above steps amounted to ca.\ 20 min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software.

\paragraph{Baseline} ...
